### 2013-01-20 edupar-13/outcomes.tex
outcomes.tex: Mention here that volunteers were "top students", not random.

We evaluated Landslide in two ways: first, by instrumenting two prior-semester student kernels to measure the exploration time needed to find different races, and second, by meeting with current-semester students, before they submitted their kernel for grading, to see if they could find bugs on their own with Landslide.

>>>>

We evaluated Landslide in two ways: first, by instrumenting two prior-semester student kernels to measure the exploration time needed to find different races, and second, by meeting with current-semester student volunteers, before they submitted their kernel for grading, to see if they could find bugs on their own with Landslide.
(The volunteers were chosen from students with free time, i.e., were not chosen at random.)
